---
output:
  html_notebook: default
  html_document: default
---
```{r}
library(rollRegres)
library(ggpubr)
```
Data Input: price_calulations.csv & volume_calculations.csv + calculated hourly returns, reshaped y1,y2,y3 values.
```{r}
price_data_input <- "price_returns.csv"
volume_data_input <- "volume_returns.csv"

price_data <- read.csv(price_data_input)
volume_data <- read.csv(volume_data_input)
```
Create dataframes for storing predicted returns to compare to real returns.
```{r}
predicted_price_return <- data.frame(price_data['timestamp'])
predicted_price_return['real_return'] <- price_data['return']

predicted_volume_return <- data.frame(volume_data['timestamp'])
predicted_volume_return['real_return'] <- volume_data['return']
```
PRICE RETURN REGRESSIONS

Rolling Regression: Price returns on y1 
Regression period of ~425 days = 10200 hours
Predict returns on reshaped y1
```{r}
price_mdl_y1 <- roll_regres(return ~ y1, price_data, width = 10200L)
price_mdl_y1_intercepts <- price_mdl_y1$coefs[,1]
price_mdl_y1_coefs <-price_mdl_y1$coefs[,2]

predicted_price_return['return_y1'] <- price_mdl_y1_intercepts + price_mdl_y1_coefs*price_data['reshaped.y1']
```
Price returns on y1: Pearson correlation test
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y1'], method = 'pearson')
```
Price returns on y1: Kendall rank correlation test
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y1'], method = 'kendall')
```
Price returns on y1: Spearman rank correlation coefficient
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y1'], method = 'spearman')
```

Rolling Regression: Price returns on y2
```{r}
price_mdl_y2 <- roll_regres(return ~ y2, price_data, width = 10200L)
price_mdl_y2_intercepts <- price_mdl_y2$coefs[,1]
price_mdl_y2_coefs <-price_mdl_y2$coefs[,2]

predicted_price_return['return_y2'] <- price_mdl_y2_intercepts + price_mdl_y2_coefs*price_data['reshaped.y2']
```
Price returns on y2: Pearson correlation test
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y2'], method = 'pearson')
```
Price returns on y2: Kendall rank correlation test
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y2'], method = 'kendall')
```
Price returns on y2: Spearman rank correlation coefficient
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y2'], method = 'spearman')
```

Rolling Regression: Price returns on y3
```{r}
price_mdl_y3 <- roll_regres(return ~ y3, price_data, width = 10200L)
price_mdl_y3_intercepts <- price_mdl_y3$coefs[,1]
price_mdl_y3_coefs <-price_mdl_y3$coefs[,2]

predicted_price_return['return_y3'] <- price_mdl_y3_intercepts + price_mdl_y3_coefs*price_data['reshaped.y3']
```
Price returns on y3: Pearson correlation test
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y3'], method = 'pearson')
```
Price returns on y3: Kendall rank correlation test
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y3'], method = 'kendall')
```
Price returns on y3: Spearman rank correlation coefficient
```{r}
cor.test(predicted_price_return[,'real_return'], predicted_price_return[,'return_y3'], method = 'spearman')
```
VOLUME RETURN REGRESSIONS

Rolling Regression: Volume returns on y1 
```{r}
volume_mdl_y1 <- roll_regres(return ~ y1, volume_data, width = 10200L)
volume_mdl_y1_intercepts <- volume_mdl_y1$coefs[,1]
volume_mdl_y1_coefs <-volume_mdl_y1$coefs[,2]

predicted_volume_return['return_y1'] <- volume_mdl_y1_intercepts + volume_mdl_y1_coefs*volume_data['reshaped.y1']
```
Volume returns on y1: Pearson correlation test
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y1'], method = 'pearson')
```
Volume returns on y1: Kendall rank correlation test
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y1'], method = 'kendall')
```
Volume returns on y1: Spearman rank correlation coefficient
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y1'], method = 'spearman')
```
Rolling Regression: Volume returns on y2
```{r}
volume_mdl_y2 <- roll_regres(return ~ y2, volume_data, width = 10200L)
volume_mdl_y2_intercepts <- volume_mdl_y2$coefs[,1]
volume_mdl_y2_coefs <-volume_mdl_y2$coefs[,2]

predicted_volume_return['return_y2'] <- volume_mdl_y2_intercepts + volume_mdl_y2_coefs*volume_data['reshaped.y2']
```
Volume returns on y2: Pearson correlation test
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y2'], method = 'pearson')
```
Volume returns on y2: Kendall rank correlation test
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y2'], method = 'kendall')
```
Volume returns on y2: Spearman rank correlation coefficient
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y2'], method = 'spearman')
```
Rolling Regression: Volume returns on y3
```{r}
volume_mdl_y3 <- roll_regres(return ~ y3, volume_data, width = 10200L)
volume_mdl_y3_intercepts <- volume_mdl_y3$coefs[,1]
volume_mdl_y3_coefs <-volume_mdl_y3$coefs[,2]

predicted_volume_return['return_y3'] <- volume_mdl_y3_intercepts + volume_mdl_y3_coefs*volume_data['reshaped.y3']
```
Volume returns on y3: Pearson correlation test
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y3'], method = 'pearson')
```
Volume returns on y3: Kendall rank correlation test
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y3'], method = 'kendall')
```
Volume returns on y3: Spearman rank correlation coefficient
```{r}
cor.test(predicted_volume_return[,'real_return'], predicted_volume_return[,'return_y3'], method = 'spearman')
```
